### 2019-01-10 pkg/colorspace/index.Rmd
improvements in vignettes/www
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@370 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
h2 title on index page (due to new font)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@406 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
employ ag_Synset (rather than Heat) on index page to correspond to logo/favicon
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@412 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

### A Toolbox for Manipulating and Assessing Colors and Palettes

@@

```{r palettes, echo = FALSE, fig.show = "hide", fig.width = 4.5, fig.height = 4.5, fig.align = "center", dev = "png", dpi = 48}
hcl_palettes(name = c(
  "Pastel 1", "Dark 3", "Harmonic",
  "Blues 3", "Greens 3", "Reds 3",
  "Heat", "Purple-Blue", "Viridis",
  "Blue-Red", "Green-Brown", "Tropic"
), plot = TRUE, n = 7)
```

@@

>>>>

## A Toolbox for Manipulating and Assessing Colors and Palettes

@@

```{r palettes, echo = FALSE, fig.show = "hide", fig.width = 4.5, fig.height = 4.5, fig.align = "center", dev = "png", dpi = 48}
hcl_palettes(palette = c(
  "Pastel 1", "Dark 3", "Harmonic",
  "Blues 3", "Greens 3", "Reds 3",
  "ag_Sunset", "Purple-Blue", "Viridis",
  "Blue-Red", "Green-Brown", "Tropic"
), plot = TRUE, n = 7)
```

@@

| Interactive color apps                         |
|:----------------------------------------------:|
| ![](articles/screenshots/choose_palette_1.png) |
